Probabilistic Model of Bilateral Lymphatic Spread in Head and Neck Cancer

### 2024-12-10 manuscript.qmd
Built site for gh-pages

import pandas as pd
import numpy as np
import matplotlib.pyplot as plt
from matplotlib import ticker
from matplotlib.colors import LinearSegmentedColormap
import upsetplot

@@

$$
P \left( \mathbf{X}^\text{c}, \epsilon=\texttt{True} \mid \tau + 1 \right) = \big[ p_\epsilon P \left( \mathbf{X}^\text{c}, \epsilon=\texttt{False} \mid \tau \right) + P \left( \mathbf{X}^\text{c}, \epsilon=\texttt{True} \mid \tau \right) \big]^\top \cdot \mathbf{A}_\text{c}^{\epsilon=\texttt{True}}
$$

@@

$$
P \big( \text{IV}^\text{c} \mid \mathbf{Z}^\text{i}=\boldsymbol{\zeta}^\text{i}_k, \mathbf{Z}^\text{c}=\boldsymbol{\zeta}^\text{c}_\ell, \boldsymbol{\hat{\theta}}, \text{T}x \big) = \sum_k \sum_{\ell \, : \, \xi_{\ell 4}=1} P \big( \mathbf{X}^\text{i} = \boldsymbol{\xi}^\text{i}_k, \mathbf{X}^\text{c} = \boldsymbol{\xi}^\text{c}_\ell \mid \boldsymbol{\zeta}^\text{i}_k, \boldsymbol{\zeta}^\text{c}_\ell, \epsilon, \boldsymbol{\hat{\theta}}, \text{T}x \big)
$$ {#eq-marg-over-posterior}

@@

involved = num_involved.join(
  100 * percent_involved,
  rsuffix=" (%)",
)
involved.columns = pd.MultiIndex.from_product(
  [["I", "II", "III", "IV"],
   ["n", "%"]],
  names=["LNL", ""]
)
involved["total", "n"] = total["I"]
(
  involved
  .reset_index()
  .sort_values(
    by=["T-cat.", "ipsi", "Mid. ext."],
    ascending=[False, True, True],
  )
  .style
  .format(precision=2)
  .apply(right_align, subset=involved.columns[0:])
  .apply(highlight_t_stage, subset=["T-cat."])
  .apply(highlight_bool, subset=["Mid. ext."])
  .apply(highlight, subset=["ipsi"], mapping={
    "0": COLORS["green"],
    "1": COLORS["orange"],
    "≥ 2": COLORS["red"],
  })
  .hide()
)
```

>>>>

import pandas as pd
import numpy as np

@@

$$
\begin{multlined}
P \left( \mathbf{X}^\text{c}, \epsilon=\texttt{True} \mid \tau + 1 \right) \\
= \big[ p_\epsilon P \left( \mathbf{X}^\text{c}, \epsilon=\texttt{False} \mid \tau \right) + P \left( \mathbf{X}^\text{c}, \epsilon=\texttt{True} \mid \tau \right) \big]^\top \cdot \mathbf{A}_\text{c}^{\epsilon=\texttt{True}}
\end{multlined}
$$

@@

$$
\begin{multlined}
P \big( \text{IV}^\text{c} \mid \mathbf{Z}^\text{i}=\boldsymbol{\zeta}^\text{i}_k, \mathbf{Z}^\text{c}=\boldsymbol{\zeta}^\text{c}_\ell, \boldsymbol{\hat{\theta}}, \text{T}x \big) \\
= \sum_k \sum_{\ell \, : \, \xi_{\ell 4}=1} P \big( \mathbf{X}^\text{i} = \boldsymbol{\xi}^\text{i}_k, \mathbf{X}^\text{c} = \boldsymbol{\xi}^\text{c}_\ell \mid \boldsymbol{\zeta}^\text{i}_k, \boldsymbol{\zeta}^\text{c}_\ell, \epsilon, \boldsymbol{\hat{\theta}}, \text{T}x \big)
\end{multlined}
$$ {#eq-marg-over-posterior}

@@

involved = num_involved.join(
  100 * percent_involved,
  rsuffix=" (%)",
)
involved = involved.reindex(sorted(involved.columns), axis="columns")
involved.columns = pd.MultiIndex.from_product(
  [["I", "II", "III", "IV"],
   ["n", "%"]],
  names=["LNL", ""]
)
involved["total", "n"] = total["I"]
(
  involved
  .reset_index()
  .sort_values(
    by=["T-cat.", "ipsi", "Mid. ext."],
    ascending=[False, True, True],
  )
  .style
  .format(precision=2)
  .apply(right_align, subset=involved.columns[0:])
  .apply(highlight_t_stage, subset=["T-cat."])
  .apply(highlight_bool, subset=["Mid. ext."])
  .apply(highlight, subset=["ipsi"], mapping={
    "0": COLORS["green"],
    "1": COLORS["orange"],
    "≥ 2": COLORS["red"],
  })
  .hide()
)
```
